---
title: "R Markdown Assignment"
author: "Varun Teja Kolluru"
date: "`r Sys.Date()`"
output:
  word_document: default
  html_document: default
---

### Remove the list in environment window
```{r}
rm(list=ls())
```

### Add the libraries which are used in the code
```{r}
library(rio)
library(moments)
```

### Load the file from the directory
```{r}
my_data = import('test.xlsx')
```

### change the column names to lower case
```{r}
colnames(my_data) = tolower(make.names(colnames(my_data)))
```

### Creating a new subset for states with Washington and Georigia
```{r}
sub_data = subset(my_data,state=='WA'|state=='GA')
```

### Creating a seed with my U number and create a sample from subset
```{r}
set.seed('97')
my_sample = sub_data[sample(1:nrow(sub_data),60),]
attach(my_sample)
```
The above code is a pre processing code, which gets the data from the given file and creating a subset and using the subset data a new sample is created with seeding number. 

### Below is the sample data
```{r}
my_sample
```



# Start of analysis
### Structure of the data object
```{r}
str(my_sample)
```

### Mean Median SD skewness kurtosis
```{r}
mean(price)
median(price)
sd(price)
skewness(price)
kurtosis(price)
```
```{r echo=FALSE}
skew <- skewness(price)
kur = kurtosis(price)
```
We got skewness as `r ifelse(skew>0, "Positive", "Negative")` value, which is a `r ifelse(skew>0, "Right", "Left")` skewed graph and the kurtosis is `r ifelse(kur>3, "Above", "Below")` 3, which will be a `r ifelse(kur>3, "leptokurtic", "Platokurtic")` graph and there is a lot of standard deviation from the standard symmetric or bell shapes curve graph. 

### Boxplot for age variable
```{r}
boxplot(age,pch=19,main="Box Plot for the Age variable")
```

Based on the above boxplot for the age variable, we can say that the deviation in the standard curve to Right side which is a Right skewness curve. This is due to the 4 Outliers( 4 Dots) after the 40 age limit in the Y axis in the graph. In detail, 25% quartile starts after ‘10’ and the 75% quartile ends at some where ‘24’ and the median is `r median(price)`. And based on this graph we can infer that most of the boats are aged in between 10 to 25. 

### Qunatile for age variable
```{r}
quantile(age,probs = seq(0,1,0.20))
```


### Histogram for the length variable
```{r}
hist(length,col="blue",main="Histogram for Lenght varible with better look and feel",
     xlim = c(0,150))
```


By viewing this histogram graph for length variable, we can say that this do not follow a symmetric shaped curve. We can say that this is a `r ifelse(skew>0, "Right", "Left")` skewed curve. And if we closely observe the graph, after the ‘100’, there is a raise in the graph and this might be a double curved graph. 

### stem and leaf plot for age variable
```{r}
plot(density(age),lwd=3,main="Plot for age variable")
plot(age,pch=19)
```

### Boxplot comparing prices for GA and WA state
```{r}
my.ga = subset(my_data,state=='GA')
my.wa = subset(my_data,state=='WA')
boxplot(my.ga$price,my.wa$price,pch=19,
        main="GA state price vs WA state price",
        col=c("red","red"),names=c("Georgia","Washington"))
```
